paper

### 2024-09-26 inst/extdata/paperdata/paper.qmd
.

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 2000  # Number of bootstrap samples
K <- dim(soma)[1]/2  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

limrots.result <- LimROTS(data.exp = soma, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

@@

```{r}
limrots.result.df <- data.frame(proteins = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$corrected.logfc,
                                q = limrots.result$q_values$qvalues)
limrots.result.df <- limrots.result.df[limrots.result.df$q < 0.05,]
```

>>>>

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

@@

limrots.result2 <- LimROTS(data.exp = soma, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)

@@

```{r}
limrots.result.df <- data.frame(proteins = row.names(limrots.result$data),
                                LimROTS.FC = limrots.result$corrected.logfc,
                                q = limrots.result$q_values$qvalues,
                                p.value = limrots.result$pvalue)

limrots.result.df <- limrots.result.df[limrots.result.df$q < 0.05,]
```

```{r}
set.seed(1234, kind = "default")

soma0.5 <- soma[, sample(1:262, 262) , drop = FALSE]

set.seed(1234, kind = "default")
keep_samples <- colData(soma0.5)$CNO != 12
soma0.5 <- soma0.5[, keep_samples]

# Set metadata and formula for LimROTS analysis
meta.info <- names(soma0.5@colData@listData)
B <- 1000  # Number of bootstrap samples
K <- dim(soma0.5)[1]/4  # Set the value for K based on the data size
K <- floor(K) 
num_cores <- 30  # Number of cores for parallel processing
cluster <- makeCluster(num_cores)  # Create a parallel cluster
group.name <- "group_comp"
formula.str <- "~ 0 + group_comp + gender + AGE + CNO + pc1 + pc2 + pc3 + pc4"  # Formula for group comparison
# Run LimROTS analysis with trend and robust settings enabled

soma0.5@colData@listData[["CNO"]] <- paste0("CNO" , soma0.5@colData@listData[["CNO"]])

soma0.5@colData@listData[["CNO"]] <- as.factor(soma0.5@colData@listData[["CNO"]])

limrots.result2 <- LimROTS(data.exp = soma0.5, 
                          B = B, K = K, meta.info = meta.info, 
                          cluster = cluster, group.name = group.name, 
                          formula.str = formula.str, trend = TRUE, robust = TRUE, progress = TRUE, seed.cl = 1234)
